Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-02-08 paper/paper.Rmd
Added results

>>>>

Average seed locations provided a metric for seed dispersal in each simulation run, and seed dispersion shows how far apart each of the seeds are from each other in every simulation run. We show average seed locations and seed dispersion for the three models (Figure 4B-C) and although the average measures for these are comparable between models, location and dispersion have a greater number of outliers in the indvidual and family models. This suggests that although the average measures are similar between models, the variation between them is different, with the individual and family models showing both a greater maximum dispersal distance, and a higher percentage of long-distance dispersal events (Table 1.) Interestingly, the higher percentage of LDD events in the individual kernels also has a higher standard deviation, a result of the variation in the dispersal kernels produced by each bird (Figure 4A), where some birds or social groups where characteristically long-dispersers versus individuals with shorter dispersal distances and even one individual for which simulated seed dispersal distances were all below 500m (Supplementary information).

## Kernel functions for frugivore-generated dispersal distances

For the seed dispersal data generated from each of the three simulation models, we fit a Weibull distribution function and estimated the parameters for each of the models (Table 2). The shape parameters provided information on the fatness of the tails, as previously mentioned in the methods section above. Although all three models have shape parameters $>1$, describing thin tails, we find that there are differences between the three simulation models, with the null model having the largest shape parameter value and thus showing the thinnest tail among the three models (Figure 5). The individual model shows the smallest shape parameter value, and thus describing the dispersal kernel with the heaviest tail among the three models.

Given our interest in long-distance dispersal events and the potential to use statistics of extremes in seed dispersal ecology, we fit the data of the three simulated models to a generalized Pareto distribution following a peak-over-threshold approach. Using this approach, we also performed analysis with threshold diagnostic plots and mean residual life plots (Supplementary information) to estimate the best thresholds for our data. These type of diagnostic approach helps us identify the distances above which we can consider seed dispersal events as long-distance dispersal. We report these threshold values, and parameter estimates (Table 3.) showing that all three dispersal kernels have shape parameter values $<0$ thus corresponding to thin tails, following a Beta distribution with an upper limit. Although the parameter estimates are close and they show thin tail for all three models, the generalized Pareto fit shows a similar trend as that in the Weibull kernels, with the individual model showing a fatter tail, followed by the family model, and the null model with the thinnest tail (Figure 6). Using these parameter values, we calculated the probabilities of long-distance dispersal events at different distances from the parent tree (Table 4), ranging from 250 to 2000m over the threshold. Although these are very low probabilities, it is worth noting that the parameters associated with the null model reach a zero probability of dispersal for seeds beyond 1250m conditional on the null threshold, whereas the individual level model has probabilites greater than zero for dispersal events of 1750m beyond the threshold ($P(X=1750) = 2e^-7$). All three models had a probability of zero for dispersal events greater than 2000 meters beyond the LDD threshold.
